Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species

### 2016-12-15 ms/Accessory/Wenk-Accessory-SI.Rnw
Example printing data from _meta.csv files

print_table_species <- function(species, data) {
  data <- data[data$species == species, -c(1)]
  print(xtable(data,
            hline.after=c(1),
            align='p{0.1cm}p{4cm}p{6cm}p{2.5cm}p{1cm}p{1cm}',
            label=sprintf("tab:parts_%s", species),
            caption=sprintf("Table of parts for %s.", species)),
      sanitize.text.function=I,
      , table.placement = "H"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)
}

@@

2013\_Kuringgai\_harvest
Allometric data for plants harvested in autumn 2013, including weights and diameters of each harvested segment. Briefly, this dataset includes data on 14 dominant species that are all obligate seeders following a fire. For each species, data were collected from 7 replicate individuals at each of 6 sites, or the subset of those sites on which a given species occurred. The sites represent a chronosequence created by a patchy fire history in the area; all species germinate within a year of a fire, allowing fire history to be used as a proxy for age. When the plants were harvested, they were divided into multiple segments along the stem leader. The diameter was measured at each cut in autumn 2012, when the plants were tagged, and in autumn 2013, at harvest.  For each segment, the dry weights of the leaves and stems were determined separately.

@@

Flower\_parts-meta
Brief descriptions of each data column in the file flower\_parts, including units.

>>>>

print_table_species <- function(species, data) {
  data <- data[data$species == species, -c(1)]
  print(xtable(data,
            hline.after=c(1),
            align='p{0.1cm}p{4cm}p{6cm}p{2.5cm}p{1cm}p{1cm}',
            label=sprintf("tab:parts_%s", species),
            caption=sprintf("Table of parts for %s.", species)),
      sanitize.text.function=I,
      , table.placement = "h"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)
}

print_table_metadata <- function(path) {

  data <-  read.csv(path, stringsAsFactors=FALSE, check.names=FALSE)
  file <- gsub("_", "\\_", basename(path), fixed = TRUE)
  print(xtable(data,
            hline.after=c(1),
            label=sprintf("tab:file_", file),
            caption=
              sprintf("Variables within the file `%s`. These definitions are defined within the file `%s` in the folder `data`.",
              gsub("\\_meta", "", file, fixed = TRUE), file)),
      , table.placement = "h"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)
}

@@

\subsection{Harvest}

Allometric data for plants harvested in autumn 2013, including weights and diameters of each harvested segment. Briefly, this dataset includes data on 14 dominant species that are all obligate seeders following a fire. For each species, data were collected from 7 replicate individuals at each of 6 sites, or the subset of those sites on which a given species occurred. The sites represent a chronosequence created by a patchy fire history in the area; all species germinate within a year of a fire, allowing fire history to be used as a proxy for age. When the plants were harvested, they were divided into multiple segments along the stem leader. The diameter was measured at each cut in autumn 2012, when the plants were tagged, and in autumn 2013, at harvest.  For each segment, the dry weights of the leaves and stems were determined separately.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/harvest_meta.csv")
@

@@

\subsection{Flower\_parts}
Brief descriptions of each data column in the file flower\_parts, including units.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/flowerParts_meta.csv")
@
